\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2018-09-30 paper.tex

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbunding, less trust and
commodification of services, such as payments for per-megabyte internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

%Diagram - Broken funding transaction
\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/funding-broken2.pdf}
	}
	\caption{Either of the Commitment Transactions can be broadcast any any
		time by either party, only one will successfully spend from the
		single Funding Transaction. This cannot work because one party
		will not want to broadcast the most recent transaction.
	}
\end{figure}

>>>>

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbundling, less trust and
commodification of services, such as payments for per-megabyte internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

%Diagram - Broken funding transaction
\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/funding-broken2.pdf}
	}
	\caption{Either of the Commitment Transactions can be broadcast any
		time by either party, only one will successfully spend from the
		single Funding Transaction. This cannot work because one party
		will not want to broadcast the most recent transaction.
	}
\end{figure}
